Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-20 revision_plan.tex
update top-level concerns

\noindent\textcolor{blue}{\textbf{Response 1:} 
Thanks for the reviewer's comments. 
The proactive transports proactively allocate the bottleneck link bandwidth and prioritize it to flows with fewer remaining bytes.
Proactive transport typically displays the performance of the large and small flows, respectively. 
To support our claim of "comparable performance to proactive transports."
First, we compare the overall performance of the different transports through the overall average FCT.
Second, we show the average FCT and 99th percentile tail FCT for small flows to illustrate the ability of different transport to avoid small flow packet scheduling and queuing delays.
Finally, we show the average FCT for large flows to display the gap between different schemes' ability to utilize the spare bandwidth gracefully.
These are the performance metrics that proactive transports focus on and work with.
Therefore, we use them as the primary performance metrics for simulation and testbed and conclude they are comparable to performance in proactive transport.
To show more details, we have shown the lines of code required to be modified to deploy PPT and Homa-Linux, respectively (Tables 3 and 4), and the CPU usage of PPT and DCTCP under different loads (Figure 21) in the appendix.
We believe that the above performance metrics support our proposed goals well.
  }

@@

\noindent\textcolor{blue}{\textbf{Response 2:} 
Thanks for the reviewer's comments. 
PCC Proteus divides flows into primary and scavenger flows according to different application requirements and proactively reduces scavenger flow bandwidth to minimize the impact on the primary flow, thus improving the overall user experience.
By contrast, PPT is insensitive to the application type.
In PPT, all flows equally utilize the bandwidth.
PPT's proposed purpose of buffer-aware flow scheduling is to ensure that small flows bypass queued packets of most large flows in the network to optimize the FCT.
Therefore, PPT and PCC Proteus are two lines of work due to different flow behaviors and optimization goals.
We will add a discussion of PCC Proteus and other related work in Appendix B.
}

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
Thanks for the reviewer’s comments. 
In the overall average performance analysis in Section 6.2, we mentioned that the PPT benefits from gracefully utilizing the spare bandwidth without causing bandwidth waste or sending opportunistic packets too aggressively.
To further explain the insights, we add a remark at the end of Appendix C.1 to analyze how the PPT achieves its superior performance in more detail.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
Thanks for the reviewer's comments. 
We implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator.
It doesn't include the component in Swift that handles endpoint congestion because (1) PPT doesn't focus on endpoint congestion, and (2) the ns3 simulator hardly simulates endpoint congestion as well as it does. 
We compared this variant with the original delay-based transport and plotted the result in Figure 26.
We find that when incorporating PPT's design with the original delay-based transport, the overall average FCT, the average//tail FCT of small flows, and the average FCT of large flows can be reduced by 16.7\%, 56.5\%/72.1\%, and 11\%, respectively.
To show more details, we plan to add a more detailed description of this variant in the corresponding section of Appendix C.3.
We also plan to add a remark paragraph at the end of the chapter to discuss how delay-based transport can benefit from the design of the PPT in further depth.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
Thanks for the reviewer’s comments. 
We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
Another question is about specific TCP send buffer thresholds.
To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
We plot the results in Figure 20, showing that this improves the small flow performance as expected.
In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.
}

>>>>

\noindent\textcolor{blue}{\textbf{Response 1:} 
Thanks for the reviewer's comments. 
We aim to explore a new transport that can achieve comparable performance to proactive transports while being readily deployable.
To this point, we start with DCTCP and use LCP to gracefully utilize the available bandwidth. Moreover, we complement its design with a buffer-aware flow scheduling to optimize small flow’s performance.
We then show that PPT can achieve performance comparable to proactive transports by overall average, small flow average/ tail, and large flow average FCT.
We proved the readily deployable nature of PPT by implementing PPT based on Linux-kernel and low CPU overhead.
The above performance metrics can back up our design goals.
%The proactive transports proactively allocate the bottleneck link bandwidth and prioritize it to flows with fewer remaining bytes.
%Proactive transport typically displays the performance of the large and small flows, respectively. 
%To support our claim of "comparable performance to proactive transports."
%First, we compare the overall performance of the different transports through the overall average FCT.
%Second, we show the average FCT and 99th percentile tail FCT for small flows to illustrate the ability of different transport to avoid small flow packet scheduling and queuing delays.
%Finally, we show the average FCT for large flows to display the gap between different schemes' ability to utilize the spare bandwidth gracefully.
%These are the performance metrics that proactive transports focus on and work with.
%Therefore, we use them as the primary performance metrics for simulation and testbed and conclude they are comparable to performance in proactive transport.
%To show more details, we have shown the lines of code required to be modified to deploy PPT and Homa-Linux, respectively (Tables 3 and 4), and the CPU usage of PPT and DCTCP under different loads (Figure 21) in the appendix.
%We believe that the above performance metrics support our proposed goals well.
  }

@@

\noindent\textcolor{blue}{\textbf{Response 2:} 
Thanks for the reviewer's comments. 
We will add a discussion of PCC Proteus and other related work in Appendix B.
However, note that PCC Proteus and PPT are two lines of work, so we have yet to discuss it.
PCC Proteus divides flows into primary and scavenger flows according to different application requirements and proactively reduces scavenger flow bandwidth to minimize the impact on the primary flow, thus improving the overall user experience.
By contrast, PPT is insensitive to the application requirements and treats all flows equally.
PPT uses a dual-loop rate control design to utilize the available bandwidth gracefully and further complements its design with a buffer-aware flow scheduling to optimize small flow's performance.
}

@@

\noindent\textcolor{blue}{\textbf{Response 3:} 
Thanks for the reviewer’s comments. 
We will provide a more detailed discussion of how the system can deliver the performance benefits.
PPT uses LCP to gracefully utilize the spare bandwidth left by DCTCP in the slow start and queue buildup phases.
In particular, we will add further discussion for the queue buildup phase to show more details in Section 2.3.
Furthermore, we complement buffer-aware flow scheduling to optimize the performance of small flows.
We will also add a discussion of buffer-aware flow scheduling in Appendix Section 3.1.
%In the overall average performance analysis in Section 6.2, we mentioned that the PPT benefits from gracefully utilizing the spare bandwidth without causing bandwidth waste or sending opportunistic packets too aggressively.
%To further explain the insights, we add a remark at the end of Appendix C.1 to analyze how the PPT achieves its superior performance in more detail.
}

@@

\noindent\textcolor{blue}{\textbf{Response 4:} 
Thanks for the reviewer's comments. 
Actually, we have not claimed that "integration with other transports is easy."
We claim that the design of PPT can be integrated with delay-based transport.
To this point, we implemented a delay-based transport conceptually equivalent to Swift in the ns3 simulator.
%It doesn't include the component in Swift that handles endpoint congestion because (1) PPT doesn't focus on endpoint congestion, and (2) the ns3 simulator hardly simulates endpoint congestion as well as it does. 
We compared this variant with the original delay-based transport and plotted the result in Figure 26.
We find that when incorporating PPT's design with the original delay-based transport, the overall average FCT, the average//tail FCT of small flows, and the average FCT of large flows can be reduced by 16.7\%, 56.5\%/72.1\%, and 11\%, respectively.
To show more details, we plan to add a more detailed description of this variant and discuss how delay-based transport can benefit from the design of the PPT in Appendix C.3.
%We also plan to add a remark paragraph at the end of the chapter to discuss how delay-based transport can benefit from the design of the PPT in further depth.
}

@@

\noindent\textcolor{blue}{\textbf{Response 5:}
Thanks for the reviewer’s comments.
We will complete the missing details about the experimental setup and parameters in the form of tables or footnotes.
%We record the maximum value of the window from the beginning of the flow until now as MW (Maximum Window).
%Section 2.3 first shows how much DCTCP can benefit from padding the spare bandwidth to MW and plots the results in Figure 2.
%Moreover, we show that padding the spare bandwidth to MW is just suitable without wasting bandwidth or causing congestion throughout the experiment, and we plot the results of our experiment in Figure 3.
%Another question is about specific TCP send buffer thresholds.
%To reproduce the behavior of the actual deployed application as much as possible, we selected specific application traces for the Memcached application and the web server application, respectively.
%The flow size distribution in specific application traces is concentrated in particular intervals, e.g., there is no flow in the ETC trace of the paper[8] that exceeds 100KB.
%Under such traces, we set different thresholds depending on the traces to verify the effectiveness of the buffer-aware flow identification.
%In the large-scale simulation and testbed, the TCP send buffer threshold is set to the fixed value of 100KB, with outstanding results.
%To evaluate if this can benefit PPT’s performance, we construct a PPT variant that turns off this approach and considers all flows non-identified.
%We plot the results in Figure 20, showing that this improves the small flow performance as expected.
%In summary, the TCP send buffer threshold does not assume that the application type and flow size distribution are known a priori and effectively improves small flow performance.
}
